---
title: "Pizza Data Analysis"
author: "Eszter - Viki - Ozan"
date: '2020 October 23'
output: pdf_document
font: 10
 # prettydoc::html_pretty:
  #  theme: cayman
   # highlight: github
---

```{r setup, include=FALSE}
# make sure the environment is clean and call the libraries used later

rm(list=ls())
   
library(tidyverse)
library(moments)
library(xtable)
library(ggpubr)
```

## Data Collection
Due to the pandemic situation, the data collection was made exclusively online, thereby, the time spent on research reduced significantly. Due this reason, several values such as number of tables and waiters, the size of the restaurant measured by square meter were excluded in the end. The aim of those data was to examine the exclusivity of restaurant which was solved by collecting different rating on websites. On the other hand, some data on prices were less excessive in smaller restaurants that do not delivery and are also absent on the internet which might influence the outcome of the analysis negatively. 
The main purpose of the analysis is to investigate the differences in cola and margarita prices on Budapest and countryside cities such as Debrecen, Nyíregyháza, Szeged, etc. In the following parts, the result of the full anylsis will be presented shortly and a hypothesis regarding the pizza prices

```{r, include=FALSE, warning=FALSE, message=FALSE}
# importing the data

da1_url <- "https://raw.githubusercontent.com/DiamantEszter97/CEU-Business-Analytics-2020/master/Assignments/DataAnalysis1_Coding1/data/clean/da1_data.csv"
da1_data <- read_csv(da1_url)

```


```{r, include=FALSE}
#### Cola calculations to be able to ha descriptive statistics for them
## as we had few observation of 500ml cola prices we decided to calculate estimated values from the other sized products as well, for this we assumed price/ml is the same for all cola products

# merge Pepsi and Coke prices for actual 500ml columns to have the price of cola
da1_data$cola_price_500ml <- with(da1_data,ifelse(is.na(coke_price_500ml),pepsi_price_500ml,coke_price_500ml))


# calculate the estimated price of a 500ml cola based on the prices of smaller or larger quantities 
da1_data$coke_price_estimate <- (da1_data$coke_price/da1_data$size_if_not_500ml*0.5)
da1_data$pepsi_price_estimate <- (da1_data$pepsi_price/da1_data$size_if_not_500ml*0.5)

# merge these estimated columns for Pepsi and Coke
da1_data$cola_estimated_price_500ml <- with(da1_data,ifelse(is.na(coke_price_estimate),pepsi_price_estimate,coke_price_estimate))

#Delete unnecessary columns as we have the data in the merged column 
da1_data$coke_price_estimate <- NULL
da1_data$pepsi_price_estimate <- NULL

# Merge estimated values with real 500ml values to have the final 500ml price column for cola
da1_data$cola_price <- with(da1_data,ifelse(is.na(cola_price_500ml),cola_estimated_price_500ml,cola_price_500ml))


#### Variables
# cola_price_500ml contains the merged values from 500ml cola products
# cola_estimated_price_500ml contains the price which were estimated from other sized cola products
# cola_price contains all the original 500ml and estimated 500ml prices
```

## Descriptive statistics
The below table contains a summary about the main statistic connected to the collected data about the margarita pizza and cola prices. The dataset includes a total of 69 observation from which the following was concluded: the distribution is asymmetric considering the fact it possesses a positive skewness which also suggest a right long tail. However, due to the problem of collecting unified prices on 500 ml Cola, the summary also shows a conclusion of all the cola also an estimated price of them. In other words, the estimated cola prices were assumed by calculating the price/500 ml.

```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }
# descriptive summary table for margarita prices
pizza_summary_1 <- da1_data %>% 
  summarise(mean = mean(margarita_price),
            median   = median(margarita_price),
            std      = sd(margarita_price),
            iq_range = IQR(margarita_price), 
            min      = min(margarita_price),
            max      = max(margarita_price),
            skew     = round(skewness(margarita_price), digit=4),
            numObs   = sum( !is.na( margarita_price ) ) )
pizza_summary_2 <- data.frame(variable = "Margarita Pizza")
pizza_summary_1 <- cbind(pizza_summary_2, pizza_summary_1)

# descriptive summary table for cola (actual 500ml and estimated 500ml prices as well) 
cola_summary_2 <- da1_data %>% 
  summarise(mean = mean(cola_price, na.rm = TRUE),
            median   = median(cola_price, na.rm = TRUE),
            std      = sd(cola_price, na.rm = TRUE),
            iq_range = IQR(cola_price, na.rm = TRUE), 
            min      = min(cola_price, na.rm = TRUE),
            max      = max(cola_price, na.rm = TRUE),
            skew     = round(skewness(cola_price, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_price) ) )
cola_summary_3 <- data.frame(variable = "Cola")  
cola_summary_2 <- cbind(cola_summary_3, cola_summary_2)  

price_summary <- pizza_summary_1 %>% add_row( cola_summary_2 )

   
xtb <- xtable(price_summary,type = "latex", caption = "Summary statistics for the margarita  and cola prices")
print(xtb, comment=FALSE, include.rownames=FALSE)
```


```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE}
# Descriptive statistics for actual 500ml and estimated 500ml cola prices to see if the price/ml is actually the same or not

cola_500ml <- da1_data %>% 
  summarise(mean = mean(cola_price_500ml, na.rm = TRUE),
            median   = median(cola_price_500ml, na.rm = TRUE),
            std      = sd(cola_price_500ml, na.rm = TRUE),
            iq_range = IQR(cola_price_500ml, na.rm = TRUE), 
            min      = min(cola_price_500ml, na.rm = TRUE),
            max      = max(cola_price_500ml, na.rm = TRUE),
            skew     = round(skewness(cola_price_500ml, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_price_500ml) ) )
cola_500ml_1 <- data.frame(variable = "500ml Cola Actual")
cola_500ml <- cbind(cola_500ml_1, cola_500ml)

cola_est <- da1_data %>% 
  summarise(mean = mean(cola_estimated_price_500ml, na.rm = TRUE),
            median   = median(cola_estimated_price_500ml, na.rm = TRUE),
            std      = sd(cola_estimated_price_500ml, na.rm = TRUE),
            iq_range = IQR(cola_estimated_price_500ml, na.rm = TRUE), 
            min      = min(cola_estimated_price_500ml, na.rm = TRUE),
            max      = max(cola_estimated_price_500ml, na.rm = TRUE),
            skew     = round(skewness(cola_estimated_price_500ml, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_estimated_price_500ml) ) )
cola_est_1 <- data.frame(variable = "500ml Cola Estimated")
cola_est <- cbind(cola_est_1, cola_est)
cola_summary <- cola_500ml %>%  add_row(cola_est) 

xtb2 <- xtable(cola_summary,type = "latex", caption = "Summary statistics for the actual 500ml cola prices and the estimated ones")
print(xtb2, comment=FALSE, include.rownames=FALSE)


rm( pizza_summary_1, cola_summary_2, cola_500ml, cola_est, pizza_summary_2, cola_summary_3 )
```

```{r, include= FALSE, warning=FALSE}
# Changing imported_wine into a factor 
da1_data$imported_wine <- as.factor(da1_data$imported_wine)
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "0", "No")
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "no", "No")
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "yes", "Yes")

# Create new column for city (Budapest, Rest_of_Hungary)
da1_data$is_budapest <- ifelse(da1_data$city == "Budapest", "Budapest", "Rest of Hungary") 


```

## Distribution of Margarita and cola prices

As it was mentioned before, the statistics suggested a right long tail, a positive skewness which is presented in the following histograms. The main difference between the cola histograms are that the left contains the estimated prices of all colas in 500 ml units while the right shows all of the prices even if they are 330ml, 1000ml or 1250ml bottle.
The central tendency of the prices of margarita pizza are between 1400 HUF and 1600 HUF while it is around 350 HUF and 400 HUF for the estimated cola prices. On the other hand, there is an unusual increase at 600 HUF in estimated cola prices which might require further analysis in the future because the high tendency suggest a serious reason behind it.

```{r, echo=FALSE, out.width = '35%', warning=FALSE}

ggplot(data=da1_data, aes(x=margarita_price))+
  geom_histogram( aes(y = ..density..), fill="dodgerblue4", binwidth = 100)+
  geom_density(aes(y=..density..), fill="dodgerblue", alpha=0.4) +
  labs(x="Price of Margarita pizza (HUF)", y="Density") +
  theme_bw()
  
ggplot(data=da1_data, aes(x=cola_price_500ml))+
  geom_histogram( aes(y = ..density..), fill="hotpink4", binwidth = 40)+
  geom_density(aes(y=..density..), fill="hotpink", alpha=0.4) +
  labs(x="Price of 500ml Cola products (HUF)", y="Density") +
  theme_bw()+
  xlim(190,1200)

ggplot(data=da1_data, aes(x=cola_price))+
  geom_histogram( aes(y=..density..), fill="chartreuse4", binwidth = 40)+
  geom_density(aes(y=..density..), fill="chartreuse", alpha=0.4) +
  labs(x="Price of Cola products (HUF)", y="Density") +
  theme_bw()+
  xlim(190,1200)

```

## Margarita pizza prices according to their size and on restaurants with different qualities

```{r, echo = FALSE, warning = FALSE, out.width = '50%'}

# Checking the average prices of margarita pizzas per size

mean_price_32 <- mean(filter(da1_data, margarita_size == "32")$margarita_price)
mean_price_30 <- mean(filter(da1_data, margarita_size == "30")$margarita_price)

# Creating a scatterplot of Price vs Size of Margarita Pizza
price_vs_size <- ggplot( da1_data , aes( x = margarita_price , y = margarita_size ) )+
    geom_point( color = 'dodgerblue4' )+
    labs( x = 'Price of Margarita Pizza (HUF)' , y = 'Size of Margarita Pizza (cm)') + 
    geom_vline(xintercept = mean_price_32, linetype = "dashed") +
    geom_vline(xintercept = mean_price_30, color = "red", linetype = "dashed") + theme_bw()

price_vs_size + annotate("text", x = 1750, y = 28, label = "Mean Price of 32cm Pizza (HUF)") + 
  annotate("text", x = 1550, y = 29, label = "Mean Price of 30cm Pizza (HUF)", color = "red") + 
  annotate("text", x = 2150, y = 27, label = "Outlier", size = 3, color = "navyblue")

# Creating a simple boxplot for mean pizza price under imported wine category

wine_graph <- ggplot(da1_data, aes(y = margarita_price, x = imported_wine)) +
  geom_boxplot(color = "dodgerblue4", size = 0.5, width = 0.1, alpha = 0.5) +
  labs(x='Imported Wine on the Menu',y='Price') +
  theme_bw()

wine_graph + stat_boxplot(geom = "errorbar", width = 0.05,  size = 0.5) + 
   stat_summary(fun=mean, geom="point", shape=2, size=2, color="red", fill="red")
```

## Prices of Margarita pizza online vs offline and Budapest vs countryside
The following charts present the comparison of the online and offline price and the distribution of prices in Budapest and countryside. As it is presented, the delivery prices range higher than on-delivery prices while the Budapest prices excess the countryside prices.
```{r, echo=FALSE, out.width = '50%', warning=FALSE}

da1_data %>% 
  ggplot(aes(x=margarita_price, fill=delivery))+
  geom_density(aes(y=..density..), alpha=0.8) +
  labs(x="Prices of Margarity pizza (HUF)", y="Density", fill="Is it delivered or eat at the restaurant") +
  theme_bw()


da1_data %>% 
  ggplot(aes(x=margarita_price, fill=is_budapest))+
  geom_histogram( aes(y = ..density..), color="black", binwidth = 100, alpha=0.8)+
  labs(x="Prices of Margarity pizza (HUF)", y="Density", fill="Budapest or Rest of Hungary") +
  theme_bw()

```

## Hypothesis testing if the mean price online vs offline is the same
```{r, echo = FALSE}
# Welch Two Sample t-test to understand if mean pizza prices of online vs offline is different than each other 
t.test(margarita_price ~ delivery, da1_data)
```

Here we see that we reject the null hypothesis that the mean pizza price we observe online is the same as those we observe in restaurants (t = 3.0685, df = 63.384, p-value = 0.003163). The average pizza price online is 1867.200 and for those offline is 1629.769. The 95% confidence interval for the difference in prices between the two  groups is (82.82589, 392.03565).
```{r, echo = FALSE}
t.test(cola_price ~ delivery, da1_data)
```
For the difference between online and offline cola prices on the other hand, we cannot reject the null that the average of these two prices is not the same (t = 0.51646, df = 54.09, p-value = 0.6076). There is strong evidence suggesting that online and offline beverage prices are similar on average.