---
title: "Session_2"
output: html_document
output:
  rmarkdown::html_document:
    theme: lumen
---

### Create a folder somewhere and name it R_codes
### Create a project name it mentoring_2, and select the R_codes folder to base folder

### Print out the workng directory
```{r }
getwd()
```


### Download the AMZN data from ceulearning
### Save it into the working directory
### Read the data with fullpath and with relativ path
```{r }
read.csv("C:/Users/diama/Documents/CEU-Business-Analytics-2020/Coding_1/R_Codes/mentoring_2/amzn.csv")
read.csv("amzn.csv")


### How can you comment multiple lines?
```{r } ctrl + shift + c
# print your answer 
print('ctrl+shift+c')
```

### How can you add the pipe symbol?
```{r }
# print your answer 
print('Ctrl+shift+m')
```

### How can you insert code block? Why is it good?
```{r }
# print your answer 
print('Ctrl + Alt + I')
```


### install a package called rtsdata



```{r }
install.packages("rtsdata")
library(rtsdata)
ticker <- 'TSLA'
start_date <- '2020-01-01'
end_date <- Sys.Date()
df <- data.frame(ds.getSymbol.yahoo(ticker, from = start_date, to = end_date))

```

### Rename the header, to open, high,low, close, volume, adjusted,

```{r }
names(df) <- c("open", "high", "low", "close", "volume", "adjusted")
names(df)[1:6] ...
```


### Create a column which contains the dates value
```{r }
df$date_value <- row.names(df)
df[["new_column"]] <-
```


### Delete the adjusted column
```{r }
df$adjusted = NULL
```

### Create a column which indicate that is the close price is above the mean of close price use ifelse
```{r }

df$bigger <- ifelse(df$close >= mean(df$close), "yes", "no")
```

### Create a column with the year value it should be string
```{r }
df$year <- substr(df$date_value, 1, 4)
```

### Save the clean data into xlsx, csv, rds format, save table it with '#'separator as .txt 
```{r }
save(df, file = "CodingPractice_df.csv")
write.csv(df, 'tsla.csv', row.names = FALSE)
write.table()
saveRDS()
```

### Change the theme of rmd with preaty doc

