---
title: "Pizza Data Analysis"
author: "Eszter - Viki - Ozan"
date: '2020 October 23'
output: pdf_document
 # prettydoc::html_pretty:
  #  theme: cayman
   # highlight: github
---

```{r setup, include=FALSE}
# make sure the environment is clean and call the libraries used later

rm(list=ls())
   
library(tidyverse)
library(moments)
library(xtable)
library(ggpubr)
```

## Data Collection

Due to the pandemic situation, we decided to collect the data for our research exclusively from online sources. This had the advantage, that we did not have to visit several restaurants, which would have been time consuming but also caused some difficulties and also some changes in our initial set of variables. We were not able to record the area of the places, the number of waiters or the number of tables, with which we wanted to measure the ecxlusivity of the places, instead we decided to collect rating on Wolt, NetPincér, Tripadvisor, Google and also Facebook, as well as the number of reviews for reliability.
.
.
.

```{r, include=FALSE, warning=FALSE, message=FALSE}
# importing the data

da1_url <- "https://raw.githubusercontent.com/semihozankaya/CEU-Business-Analytics-2020/master/Data_Analysis1/TeamAssignment_Eszter_Ozan_Viki/da1_data.csv"
da1_data <- read_csv(da1_url)

```


```{r, include=FALSE}
#### Cola calculations to be able to ha descriptive statistics for them
## as we had few observation of 500ml cola prices we decided to calculate estimated values from the other sized products as well, for this we assumed price/ml is the same for all cola products

# merge Pepsi and Coke prices for actual 500ml columns to have the price of cola
da1_data$cola_price_500ml <- with(da1_data,ifelse(is.na(coke_price_500ml),pepsi_price_500ml,coke_price_500ml))


# calculate the estimated price of a 500ml cola based on the prices of smaller or larger quantities 
da1_data$coke_price_estimate <- (da1_data$coke_price/da1_data$size_if_not_500ml*0.5)
da1_data$pepsi_price_estimate <- (da1_data$pepsi_price/da1_data$size_if_not_500ml*0.5)

# merge these estimated columns for Pepsi and Coke
da1_data$cola_estimated_price_500ml <- with(da1_data,ifelse(is.na(coke_price_estimate),pepsi_price_estimate,coke_price_estimate))

#Delete unnecessary columns as we have the data in the merged column 
da1_data$coke_price_estimate <- NULL
da1_data$pepsi_price_estimate <- NULL

# Merge estimated values with real 500ml values to have the final 500ml price column for cola
da1_data$cola_price <- with(da1_data,ifelse(is.na(cola_price_500ml),cola_estimated_price_500ml,cola_price_500ml))


#### Variables
# cola_price_500ml contains the merged values from 500ml cola products
# cola_estimated_price_500ml contains the price which were estimated from other sized cola products
# cola_price contains all the original 500ml and estimated 500ml prices
```

## Descriptive statistics
```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }
# descriptive summary table for margarita prices
pizza_summary_1 <- da1_data %>% 
  summarise(mean = mean(margarita_price),
            median   = median(margarita_price),
            std      = sd(margarita_price),
            iq_range = IQR(margarita_price), 
            min      = min(margarita_price),
            max      = max(margarita_price),
            skew     = round(skewness(margarita_price), digit=4),
            numObs   = sum( !is.na( margarita_price ) ) )

# descriptive summary table for cola (actual 500ml and estimated 500ml prices as well) 
cola_summary_2 <- da1_data %>% 
  summarise(mean = mean(cola_price, na.rm = TRUE),
            median   = median(cola_price, na.rm = TRUE),
            std      = sd(cola_price, na.rm = TRUE),
            iq_range = IQR(cola_price, na.rm = TRUE), 
            min      = min(cola_price, na.rm = TRUE),
            max      = max(cola_price, na.rm = TRUE),
            skew     = round(skewness(cola_price, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_price) ) )
  

price_summary <- pizza_summary_1 %>% add_row( cola_summary_2 )

   
xtb <- xtable(price_summary,type = "latex", caption = "Summary statistics for the margarita  and cola prices")
print(xtb, comment=FALSE, include.rownames=TRUE)
```


```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE}
# Descriptive statistics for actual 500ml and estimated 500ml cola prices to see if the price/ml is actually the same or not

cola_500ml <- da1_data %>% 
  summarise(mean = mean(cola_price_500ml, na.rm = TRUE),
            median   = median(cola_price_500ml, na.rm = TRUE),
            std      = sd(cola_price_500ml, na.rm = TRUE),
            iq_range = IQR(cola_price_500ml, na.rm = TRUE), 
            min      = min(cola_price_500ml, na.rm = TRUE),
            max      = max(cola_price_500ml, na.rm = TRUE),
            skew     = round(skewness(cola_price_500ml, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_price_500ml) ) )

cola_est <- da1_data %>% 
  summarise(mean = mean(cola_estimated_price_500ml, na.rm = TRUE),
            median   = median(cola_estimated_price_500ml, na.rm = TRUE),
            std      = sd(cola_estimated_price_500ml, na.rm = TRUE),
            iq_range = IQR(cola_estimated_price_500ml, na.rm = TRUE), 
            min      = min(cola_estimated_price_500ml, na.rm = TRUE),
            max      = max(cola_estimated_price_500ml, na.rm = TRUE),
            skew     = round(skewness(cola_estimated_price_500ml, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_estimated_price_500ml) ) )

cola_summary <- cola_500ml %>%  add_row(cola_est) 

xtb2 <- xtable(cola_summary,type = "latex", caption = "Summary statistics for the actual 500ml cola prices and the estimated ones")
print(xtb2, comment=FALSE, include.rownames=TRUE)


rm( pizza_summary_1, cola_summary_2, cola_500ml, cola_est )
```



```{r, include= FALSE, warning=FALSE}
#### Data wrangling needed for later analysis

# Seperating the distance and the unit into two columns
da1_data <- separate(da1_data, distance, " ", into = c("distance", "distance_unit"))

# Transforming the distances to km
da1_data$distance <- ifelse(da1_data$distance_unit == "m", as.numeric(da1_data$distance)/1000, da1_data$distance)

# Renaming the distance units
da1_data$distance_unit <- str_replace(da1_data$distance_unit, "m", "km")
da1_data$distance_unit <- str_replace(da1_data$distance_unit, "kkm", "km")

# Turning distance to a numeric variable
da1_data$distance <- as.numeric(da1_data$distance)

# Changing imported_wine into a factor 
da1_data$imported_wine <- as.factor(da1_data$imported_wine)
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "0", "No")
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "no", "No")
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "yes", "Yes")

# Rename last variable as it displays the wrong name
da1_data <- rename(da1_data, margarita_price_w_delivery=margarita_price_alone)

# Create new column for city (Budapest, Rest_of_Hungary)
da1_data$is_budapest <- ifelse(da1_data$city == "Budapest", "Budapest", "Rest of Hungary") 

  

```

## Distribution of Margarita and cola prices
```{r, echo=FALSE, out.width = '35%', warning=FALSE}

ggplot(data=da1_data, aes(x=margarita_price))+
  geom_histogram( aes(y = ..density..), fill="dodgerblue4", binwidth = 100)+
  geom_density(aes(y=..density..), fill="dodgerblue", alpha=0.4) +
  labs(x="Price of Margarita pizza", y="Density") +
  theme_bw()
  
ggplot(data=da1_data, aes(x=cola_price_500ml))+
  geom_histogram( aes(y = ..density..), fill="hotpink4", binwidth = 40)+
  geom_density(aes(y=..density..), fill="hotpink", alpha=0.4) +
  labs(x="Price of 500ml Cola products", y="Density") +
  theme_bw()+
  xlim(190,1200)

ggplot(data=da1_data, aes(x=cola_price))+
  geom_histogram( aes(y=..density..), fill="chartreuse4", binwidth = 40)+
  geom_density(aes(y=..density..), fill="chartreuse", alpha=0.4) +
  labs(x="Price of Cola products ", y="Density") +
  theme_bw()+
  xlim(190,1200)

```



## Prices of Margarita pizza online vs offline
```{r, echo=FALSE, out.width = '50%', warning=FALSE}

da1_data %>% 
  ggplot(aes(x=margarita_price, fill=delivery))+
  geom_density(aes(y=..density..), alpha=0.8) +
  labs(x="Prices of Margarity pizza", y="Density", fill="Is it delivered or eat at the restaurant") +
  theme_bw()


da1_data %>% 
  ggplot(aes(x=margarita_price, fill=is_budapest))+
  geom_histogram( aes(y = ..density..), color="black", binwidth = 100, alpha=0.8)+
  labs(x="Prices of Margarity pizza", y="Density", fill="Budapest or Rest of Hungary") +
  theme_bw()

```



## Hypothesis testing if the mean price online vs offline is the same
```{r}


  


```


## Hypothesis testing if the mean price inBudapest or in Rest of Hungary is the same
```{r}



```


## Figure 1.1: Restaurant Distances From CEU
```{r, echo = FALSE, warning = FALSE, out.width = '50%' }

# Creating a graph of restaurants' distance from CEU

distance_graph <- ggplot( da1_data , aes( x = distance  ) ) +
  geom_histogram( aes(y = ..density..) , binwidth = 0.5, fill = "dodgerblue4") +
  labs(x='Distance from CEU',y='Density') + xlim(0, 8) + ylim(0, 0.5) +
  theme_bw()

distance_graph + geom_segment( aes(x = 4, y = 0, xend = 4, yend = 0.5), color = 'black', size=1) + 
  annotate("rect",xmin=4, xmax = 8, ymin=0, ymax=0.5, fill='dodgerblue', alpha=0.1, na.rm = TRUE) + 
  annotate("text", x = 6, y = 0.12, label = "Extretme value", size=3)
```

## Figure 1.2: Change in Pizza Prices
```{r, echo = FALSE, warning = FALSE, out.width = '50%'}

# Creating a simple boxplot for mean pizza price under imported wine category

wine_graph <- ggplot(da1_data, aes(y = margarita_price, x = imported_wine)) +
  geom_boxplot(color = "dodgerblue4", size = 0.5, width = 0.1, alpha = 0.5) +
  labs(x='Imported Wine',y='Price') +
  theme_bw()

wine_graph + stat_boxplot(geom = "errorbar", width = 0.05,  size = 0.5) + 
   stat_summary(fun=mean, geom="point", shape=2, size=2, color="red", fill="red")
```


## Figure 1.3: Pizza Price and Size 
```{r, echo = FALSE, warning = FALSE, out.width = '50%'}

# Checking the average prices of margarita pizzas per size

mean_price_32 <- da1_data %>% filter(margarita_size == "32") %>% summarize(mean(margarita_price))
mean_price_30 <- da1_data %>% filter(margarita_size == "30") %>% summarize(mean(margarita_price))

# Creating a scatterplot of Price vs Size of Margarita Pizza
price_vs_size <- ggplot( da1_data , aes( x = margarita_price , y = margarita_size ) )+
    geom_point( color = 'dodgerblue4' )+
    labs( x = 'Price of Margarita Pizza' , y = 'Size of Margarita Pizza') + geom_vline(xintercept = mean_price_32[[1]], linetype = "dashed") +
    theme_bw() +
  geom_vline(xintercept = mean_price_30[[1]], color = "red", linetype = "dashed")

price_vs_size + annotate("text", x = 1750, y = 28, label = "Mean Price of 32cm Pizza") + 
  annotate("text", x = 1550, y = 29, label = "Mean Price of 30cm Pizza", color = "red") + 
  annotate("text", x = 2150, y = 27, label = "Outlier", size = 3, color = "navyblue")

```


