---
title: "Pizza Data Analysis"
author: "Eszter - Viki - Ozan"
date: '2020 October 23'
output: pdf_document
 # prettydoc::html_pretty:
  #  theme: cayman
   # highlight: github
---

```{r setup, include=FALSE}
# make sure the environment is clean and call the libraries used later

rm(list=ls())
   
library(tidyverse)
library(moments)
library(xtable)
library(ggpubr)
```

## Data Collection

Due to the pandemic situation, we decided to collect the data for our research exclusively from online sources. This had the advantage, that we did not have to visit several restaurants, which would have been time consuming but also caused some difficulties and also some changes in our initial set of variables. We were not able to record the area of the places, the number of waiters or the number of tables, with which we wanted to measure the ecxlusivity of the places, instead we decided to collect rating on Wolt, NetPincér, Tripadvisor, Google and also Facebook, as well as the number of reviews for reliability.
.
.
.

```{r, include=FALSE, warning=FALSE, message=FALSE}
# importing the data

da1_url <- "https://raw.githubusercontent.com/DiamantEszter97/CEU-Business-Analytics-2020/master/Assignments/DataAnalysis1_Coding1/data/clean/da1_data.csv"
da1_data <- read_csv(da1_url)

```


```{r, include=FALSE}
#### Cola calculations to be able to ha descriptive statistics for them
## as we had few observation of 500ml cola prices we decided to calculate estimated values from the other sized products as well, for this we assumed price/ml is the same for all cola products

# merge Pepsi and Coke prices for actual 500ml columns to have the price of cola
da1_data$cola_price_500ml <- with(da1_data,ifelse(is.na(coke_price_500ml),pepsi_price_500ml,coke_price_500ml))


# calculate the estimated price of a 500ml cola based on the prices of smaller or larger quantities 
da1_data$coke_price_estimate <- (da1_data$coke_price/da1_data$size_if_not_500ml*0.5)
da1_data$pepsi_price_estimate <- (da1_data$pepsi_price/da1_data$size_if_not_500ml*0.5)

# merge these estimated columns for Pepsi and Coke
da1_data$cola_estimated_price_500ml <- with(da1_data,ifelse(is.na(coke_price_estimate),pepsi_price_estimate,coke_price_estimate))

#Delete unnecessary columns as we have the data in the merged column 
da1_data$coke_price_estimate <- NULL
da1_data$pepsi_price_estimate <- NULL

# Merge estimated values with real 500ml values to have the final 500ml price column for cola
da1_data$cola_price <- with(da1_data,ifelse(is.na(cola_price_500ml),cola_estimated_price_500ml,cola_price_500ml))


#### Variables
# cola_price_500ml contains the merged values from 500ml cola products
# cola_estimated_price_500ml contains the price which were estimated from other sized cola products
# cola_price contains all the original 500ml and estimated 500ml prices
```

## Descriptive statistics
```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }
# descriptive summary table for margarita prices
pizza_summary_1 <- da1_data %>% 
  summarise(mean = mean(margarita_price),
            median   = median(margarita_price),
            std      = sd(margarita_price),
            iq_range = IQR(margarita_price), 
            min      = min(margarita_price),
            max      = max(margarita_price),
            skew     = round(skewness(margarita_price), digit=4),
            numObs   = sum( !is.na( margarita_price ) ) )
pizza_summary_2 <- data.frame(variable = "Margarita Pizza")
pizza_summary_1 <- cbind(pizza_summary_2, pizza_summary_1)

# descriptive summary table for cola (actual 500ml and estimated 500ml prices as well) 
cola_summary_2 <- da1_data %>% 
  summarise(mean = mean(cola_price, na.rm = TRUE),
            median   = median(cola_price, na.rm = TRUE),
            std      = sd(cola_price, na.rm = TRUE),
            iq_range = IQR(cola_price, na.rm = TRUE), 
            min      = min(cola_price, na.rm = TRUE),
            max      = max(cola_price, na.rm = TRUE),
            skew     = round(skewness(cola_price, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_price) ) )
cola_summary_3 <- data.frame(variable = "Cola")  
cola_summary_2 <- cbind(cola_summary_3, cola_summary_2)  

price_summary <- pizza_summary_1 %>% add_row( cola_summary_2 )

   
xtb <- xtable(price_summary,type = "latex", caption = "Summary statistics for the margarita  and cola prices")
print(xtb, comment=FALSE, include.rownames=FALSE)
```


```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE}
# Descriptive statistics for actual 500ml and estimated 500ml cola prices to see if the price/ml is actually the same or not

cola_500ml <- da1_data %>% 
  summarise(mean = mean(cola_price_500ml, na.rm = TRUE),
            median   = median(cola_price_500ml, na.rm = TRUE),
            std      = sd(cola_price_500ml, na.rm = TRUE),
            iq_range = IQR(cola_price_500ml, na.rm = TRUE), 
            min      = min(cola_price_500ml, na.rm = TRUE),
            max      = max(cola_price_500ml, na.rm = TRUE),
            skew     = round(skewness(cola_price_500ml, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_price_500ml) ) )
cola_500ml_1 <- data.frame(variable = "500ml Cola Actual")
cola_500ml <- cbind(cola_500ml_1, cola_500ml)

cola_est <- da1_data %>% 
  summarise(mean = mean(cola_estimated_price_500ml, na.rm = TRUE),
            median   = median(cola_estimated_price_500ml, na.rm = TRUE),
            std      = sd(cola_estimated_price_500ml, na.rm = TRUE),
            iq_range = IQR(cola_estimated_price_500ml, na.rm = TRUE), 
            min      = min(cola_estimated_price_500ml, na.rm = TRUE),
            max      = max(cola_estimated_price_500ml, na.rm = TRUE),
            skew     = round(skewness(cola_estimated_price_500ml, na.rm = TRUE), digit=4),
            numObs   = sum( !is.na( cola_estimated_price_500ml) ) )
cola_est_1 <- data.frame(variable = "500ml Cola Estimated")
cola_est <- cbind(cola_est_1, cola_est)
cola_summary <- cola_500ml %>%  add_row(cola_est) 

xtb2 <- xtable(cola_summary,type = "latex", caption = "Summary statistics for the actual 500ml cola prices and the estimated ones")
print(xtb2, comment=FALSE, include.rownames=FALSE)


rm( pizza_summary_1, cola_summary_2, cola_500ml, cola_est, pizza_summary_2, cola_summary_3 )
```



```{r, include= FALSE, warning=FALSE}
# Changing imported_wine into a factor 
da1_data$imported_wine <- as.factor(da1_data$imported_wine)
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "0", "No")
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "no", "No")
da1_data$imported_wine <- str_replace(da1_data$imported_wine, "yes", "Yes")

# Create new column for city (Budapest, Rest_of_Hungary)
da1_data$is_budapest <- ifelse(da1_data$city == "Budapest", "Budapest", "Rest of Hungary") 


```

## Distribution of Margarita and cola prices
```{r, echo=FALSE, out.width = '35%', warning=FALSE}

ggplot(data=da1_data, aes(x=margarita_price))+
  geom_histogram( aes(y = ..density..), fill="dodgerblue4", binwidth = 100)+
  geom_density(aes(y=..density..), fill="dodgerblue", alpha=0.4) +
  labs(x="Price of Margarita pizza", y="Density") +
  theme_bw()
  
ggplot(data=da1_data, aes(x=cola_price_500ml))+
  geom_histogram( aes(y = ..density..), fill="hotpink4", binwidth = 40)+
  geom_density(aes(y=..density..), fill="hotpink", alpha=0.4) +
  labs(x="Price of 500ml Cola products", y="Density") +
  theme_bw()+
  xlim(190,1200)

ggplot(data=da1_data, aes(x=cola_price))+
  geom_histogram( aes(y=..density..), fill="chartreuse4", binwidth = 40)+
  geom_density(aes(y=..density..), fill="chartreuse", alpha=0.4) +
  labs(x="Price of Cola products ", y="Density") +
  theme_bw()+
  xlim(190,1200)

```

## Margarita pizza prices according to their size and on restaurants with different qualities

```{r, echo = FALSE, warning = FALSE, out.width = '50%'}

# Checking the average prices of margarita pizzas per size

mean_price_32 <- mean(filter(da1_data, margarita_size == "32")$margarita_price)
mean_price_30 <- mean(filter(da1_data, margarita_size == "30")$margarita_price)

# Creating a scatterplot of Price vs Size of Margarita Pizza
price_vs_size <- ggplot( da1_data , aes( x = margarita_price , y = margarita_size ) )+
    geom_point( color = 'dodgerblue4' )+
    labs( x = 'Price of Margarita Pizza' , y = 'Size of Margarita Pizza') + 
    geom_vline(xintercept = mean_price_32, linetype = "dashed") +
    geom_vline(xintercept = mean_price_30, color = "red", linetype = "dashed") + theme_bw()

price_vs_size + annotate("text", x = 1750, y = 28, label = "Mean Price of 32cm Pizza") + 
  annotate("text", x = 1550, y = 29, label = "Mean Price of 30cm Pizza", color = "red") + 
  annotate("text", x = 2150, y = 27, label = "Outlier", size = 3, color = "navyblue")

# Creating a simple boxplot for mean pizza price under imported wine category

wine_graph <- ggplot(da1_data, aes(y = margarita_price, x = imported_wine)) +
  geom_boxplot(color = "dodgerblue4", size = 0.5, width = 0.1, alpha = 0.5) +
  labs(x='Imported Wine on the Menu',y='Price') +
  theme_bw()

wine_graph + stat_boxplot(geom = "errorbar", width = 0.05,  size = 0.5) + 
   stat_summary(fun=mean, geom="point", shape=2, size=2, color="red", fill="red")
```


## Prices of Margarita pizza online vs offline
```{r, echo=FALSE, out.width = '50%', warning=FALSE}

da1_data %>% 
  ggplot(aes(x=margarita_price, fill=delivery))+
  geom_density(aes(y=..density..), alpha=0.8) +
  labs(x="Prices of Margarity pizza", y="Density", fill="Is it delivered or eat at the restaurant") +
  theme_bw()


da1_data %>% 
  ggplot(aes(x=margarita_price, fill=is_budapest))+
  geom_histogram( aes(y = ..density..), color="black", binwidth = 100, alpha=0.8)+
  labs(x="Prices of Margarity pizza", y="Density", fill="Budapest or Rest of Hungary") +
  theme_bw()

```



## Hypothesis testing if the mean price online vs offline is the same
```{r, echo = FALSE}
# Welch Two Sample t-test to understand if mean pizza prices of online vs offline is different than each other 
t.test(margarita_price ~ delivery, da1_data)
```

Here we see that we reject the null hypothesis that the mean pizza price we observe online is the same as those we observe in restaurants (t = 3.0685, df = 63.384, p-value = 0.003163). The average pizza price online is 1867.200 and for those offline is 1629.769. The 95% confidence interval for the difference in prices between the two  groups is (82.82589, 392.03565).
```{r, echo = FALSE}
t.test(cola_price ~ delivery, da1_data)
```
For the difference between online and offline cola prices on the other hand, we cannot reject the null that the average of these two prices is not the same (t = 0.51646, df = 54.09, p-value = 0.6076). There is strong evidence suggesting that online and offline beverage prices are similar on average.


## Hypothesis testing if the mean price inBudapest or in Rest of Hungary is the same
```{r, echo = FALSE}

t.test(margarita_price ~ is_budapest, da1_data)
```

Here we easily reject the null hypothesis that the mean pizza price we observe in Budapest is the same as those we observe in the rest of Hungary (t = 6.0714, df = 60.651, p-value = 9.022e-08). The average pizza price in Budapest is most likely to be higher than the rest of Hungary.
```{r, echo = FALSE}
t.test(cola_price ~ is_budapest, da1_data)
```
For cola prices, we again reject the null of same average prices in Budapest and the rest of Hungary but the evidence is not as strong this time (t = 2.8381, df = 54.756, p-value = 0.006354).


